---
title: "Data Analysis Regression Models"
output:
  pdf_document: default
  html_notebook: default
---
## This notebook imports my cryptocurrency data set and runs multiple regressions 

### Sources: 
1. Lecture 10 Notes 
2. Lecture 11 Notes
3. https://www.youtube.com/watch?v=xcZib3qAc30 (YouTube)
4. https://www.codecademy.com/learn/learn-linear-regression-in-r/modules/linear-regression-in-r/cheatsheet

### Preparing Data for Regressions 
```{r}
crypto_data <- read.csv("C:/Users/laura/crypto_data.csv") #imports the crypto data set
head(crypto_data) #views the first few rows 
names(crypto_data) #checks the column names 
str(crypto_data) #checks the structure of the data set
```
```{r}
crypto_data$log_market_cap <- log(crypto_data$market_cap) 
crypto_data$log_volume <- log(crypto_data$total_volume)
```

### Regression 1: Full Data Set OLS
```{r}
model1 <- lm(price_volatility ~ log_volume + log_market_cap, data = crypto_data)#runs regression using volume and market cap to explain price volatility 
summary(model1) #prints results 
```
Regression 1 Interpretation:This regression shows that both trading volume and market cap are statistically significant. Higher trading volume it tied with higher price volatility, while higher market cap is tied with lower price volatility. The R-squared is 0.1499, which means that the model explains about 14.99% of the differences in cryptocurrency volatility. 

### Regression 2: Filtered Data Set
```{r}
filtered_data <- subset(crypto_data, market_cap > 10000000000) #filters data set
model2 <- lm(price_volatility ~ log_volume + log_market_cap,data = filtered_data) #runs regression on the filtered data to see how the volume and market cap explain price volatility 

summary(model2) #prints results 
```
Regression 2 Interpretation: This filtered regression only looks at the cryptocurrencies with market caps that are above $10 billion. The results show that trading volume and market cap are not statistically significant, which means that they do not strongly explain price volatility for larger cryptocurrencies. The R-squared of of 0.028 is very low, which means that the model explains very little of the variation in volatility. 

### Regression 3: Regression using a Binary Variable 
```{r}
crypto_data$large_crypto <- ifelse(crypto_data$market_cap >= 10000000000, 1, 0) #creates a binary variable where 1 = market cap is $10B or higher and 0 = below $10B

model3 <- lm(price_volatility ~ log_volume + log_market_cap + volume_to_market_cap_ratio + large_crypto, data = crypto_data) #runs regression using market cap, volume, volume to market cap ratio, and the large crypto binary variable to explain price volatility
summary(model3)
```
Regression 3 Interpretation: This regression is statistically significant overall and explains about 22.4% of volatility. However, none of the individual variables are significant. Therefore, the results do not clearly show that larger cryptocurrencies have lower volatility.

### Creating Table using Stargazer 
```{r}
#installs stargazer into R 
install.packages("stargazer") 
library(stargazer) 

stargazer(model1, model2, model3, #uses the models needed for the table 
          type = "text",
          title = "Cryptocurrency Regression Results", #adds the title to the table 
          dep.var.labels.include = FALSE, #removes dependent variable label 
          column.labels = c("Research Model", "Filtered Model", "Preferred Model"), #adds labels to each column to the corresponding model 
          covariate.labels = c("Log Trading Volume","Log Market Cap","Volume-to-Market-Cap Ratio","Large Crypto Dummy"), #adds variable labels to the table 
          digits = 3, #rounds the numbers to three decimal places 
          out = "crypto_regression_results.txt") #saves the table into computer 
```

