---
title: "Data Analysis Regression Models"
output:
  html_notebook: default
  pdf_document: default
---
## This notebook imports my cryptocurrency data set and runs multiple regressions 

### Sources: 
1. Lecture 10 Notes 
2. Lecture 11 Notes
3. https://www.youtube.com/watch?v=xcZib3qAc30 (YouTube)
4. https://www.codecademy.com/learn/learn-linear-regression-in-r/modules/linear-regression-in-r/cheatsheet

### Preparing Data for Regressions 
```{r}
crypto_data <- read.csv("C:/Users/laura/crypto_data.csv") #imports the crypto data set
names(crypto_data) #checks the column names 
str(crypto_data) #checks the structure of the data set
```
```{r}
#logs dollar values for both market cap and total volume 
crypto_data$log_market_cap <- log(crypto_data$market_cap) 
crypto_data$log_volume <- log(crypto_data$total_volume)
```

### Regression 1: Full Data Set OLS
```{r}
model1 <- lm(price_volatility ~ log_volume + log_market_cap, data = crypto_data)#runs regression using volume and market cap to explain price volatility 
summary(model1) #prints results 
```
Regression 1 Interpretation: Market cap is significant and is linked to lower volatility. Trading volume is only weakly significant and linked to higher volatility. Therefore, the model explains about 8.58% of volatility.

### Regression 2: Filtered Data Set
```{r}
filtered_data <- subset(crypto_data, market_cap > 10000000000) #filters data set
model2 <- lm(price_volatility ~ log_volume + log_market_cap,data = filtered_data) #runs regression on the filtered data to see how the volume and market cap explain price volatility 

summary(model2) #prints results 
```
Regression 2 Interpretation: For cryptocurrencies that are above $10 billion in market cap, neither trading volume nor market cap is significant. Therefore, the model explains only about 2.1% of volatility. 

### Regression 3: Regression using a Binary Variable 
```{r}
crypto_data$large_crypto <- ifelse(crypto_data$market_cap >= 10000000000, 1, 0) #creates a binary variable where 1 = market cap is $10B or higher and 0 = below $10B

model3 <- lm(price_volatility ~ log_volume + log_market_cap + volume_to_market_cap_ratio + large_crypto, data = crypto_data) #runs regression using market cap, volume, volume to market cap ratio, and the large crypto binary variable to explain price volatility
summary(model3)
```
Regression 3 Interpretation: The model adds trading volume, market cap, volume to market cap ratio, and a large crypto dummy. None of the variables are statistically significant. The model explains about 10.1% of volatility, and it does not strongly support that larger cryptocurrencies have lower volatility. 

### Creating Table using Stargazer 
```{r}
#installs stargazer into R 
install.packages("stargazer") 
library(stargazer) 

stargazer(model1, model2, model3, #uses the models needed for the table 
          type = "text",
          title = "Cryptocurrency Regression Results", #adds the title to the table 
          column.labels = c("Research Model", "Filtered Model", "Preferred Model"), #adds labels to each column to the corresponding model 
          covariate.labels = c("Log Trading Volume","Log Market Cap","Volume-to-Market-Cap Ratio","Large Crypto Dummy"), #adds variable labels to the table 
          digits = 3, #rounds the numbers to three decimal places 
          out = "crypto_regression_results.html") #saves the table into computer 
```

